Toxic code snippets on Stack Overflow

### 2017-11-05 cloverflow-tse/cloverflow.tex
Added Baltest et al. to Related Work.

The work that are closely similar to us are studies by An et al.~\cite{An2017}
and Abdalkareem et al.~\cite{Abdalkareem2017}. An et al.~investigated clones
between 399 Android apps and Stack Overflow posts. They found 1,226 code
snippets which were reused from 68 Android apps. They also observed that there
are 1,279 cases of potential license violations. The authors rely on the
timestamp to judge whether the code has been copied from/to Stack Overflow along
with confirmations from six developers. Instead of Android apps, we investigated
clones between Stack Overflow and 111 open source projects. Their results are
similar to our findings that there exist clones from software projects to Stack
Overflow with potential licensing violations. Abdalkareem et
al.~\cite{Abdalkareem2017} detected clones between Stack Overflow posts and
Android apps from the F-Droid repository and used timestamps to
determine the direction
of copying. They found 22 apps containing code cloned from Stack Overflow. They
reported that cloned code is commonly used for enhancing existing code. Their
analysis shows that the cloned code from Stack Overflow have negative effects to
quality of the apps. The median percentage of bug fixing commits after adding
Stack Overflow code (19.09\%) is higher than before adding the code (5.96\%)
with statistical significance.
%In our work, we defined seven patterns of online code cloning and 
%performed a large-scale manual check of 3,632 clone pairs. 
%We discovered 112 clone pairs with strong evidences, 
%based on natural text in comments and post contents, that they 
%were copied from Qualitas to Stack Overflow. By comparing the 
%clones to their latest versions in the software, we found that 
%64 code snippets on Stack Overflow are outdated and possibly harmful for reuse.

>>>>

The work that are closely similar to us are studies by An et al.~\cite{An2017}
Abdalkareem et al.~\cite{Abdalkareem2017}, and Baltest et al.~\cite{Baltes2017}. 
An et al.~investigated clones
between 399 Android apps and Stack Overflow posts. They found 1,226 code
snippets which were reused from 68 Android apps. They also observed that there
are 1,279 cases of potential license violations. The authors rely on the
timestamp to judge whether the code has been copied from/to Stack Overflow along
with confirmations from six developers. Instead of Android apps, we investigated
clones between Stack Overflow and 111 open source projects. Their results are
similar to our findings that there exist clones from software projects to Stack
Overflow with potential licensing violations. Abdalkareem et
al.~\cite{Abdalkareem2017} detected clones between Stack Overflow posts and
Android apps from the F-Droid repository and used timestamps to
determine the direction
of copying. They found 22 apps containing code cloned from Stack Overflow. They
reported that cloned code is commonly used for enhancing existing code. Their
analysis shows that the cloned code from Stack Overflow have negative effects to
quality of the apps. The median percentage of bug fixing commits after adding
Stack Overflow code (19.09\%) is higher than before adding the code (5.96\%)
with statistical significance.
Baltes et al.~\cite{Baltes2017} discovered that two
third of the clones from 10 most frequently referenced Java code snippets on Stack
Overflow do not contain attributions.
%In our work, we defined seven patterns of online code cloning and 
%performed a large-scale manual check of 3,632 clone pairs. 
%We discovered 112 clone pairs with strong evidences, 
%based on natural text in comments and post contents, that they 
%were copied from Qualitas to Stack Overflow. By comparing the 
%clones to their latest versions in the software, we found that 
%64 code snippets on Stack Overflow are outdated and possibly harmful for reuse.
